Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-03 prob.tex
From: Tai, Yu-Tsung Sent: Monday, October 03, 2016 1:59 To: Hanson, Andrew J. <hansona@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Liu, Weihua <liuweih@indiana.edu> Subject: RE: Shapley 1965
Dear all, 

I typed some comments about convex, and found an IVPM which doesn't rely
on the impossible to prove it has an empty core... Keep finding more
examples... Since the computation is more and more complex, maybe I
should write a program to verify some of the computation... 

Besides, when I had a dinner with Prof. Gil Kalai, he asked about
whether we hav

If we consider $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
example~\ref{ex:three-dimensional-4-value} in appendix~\ref{sec:Examples-for-QuantumIVPM}
provides another example with an empty core. Comparing to example~\ref{ex:three-dimensional-three-value},
example~\ref{ex:three-dimensional-4-value} is closer to the Born
rule in a sense that it might only correspond to $\ket{2}$ or $\frac{\mathbb{1}}{3}$,
but not $\ket{1}$, and it is no longer valid for more precise measurement
equipment as well. In general, we believe if the measurement equipment
is more and more precise, its interval-valued probability measure
will be closer and closer to the the Born rule. In the limit case,
$\mathscr{I}=\left\{ \left\{ a\right\} \middle|a\in\left[0,1\right]\right\} $
recovers conventional Gleason's theorem and the Born rule.

@@

\end{pmatrix}=\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}

@@

Consider a general density matrix~ $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{2}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{2}}r_{ij}\ket{i}\bra{j}$.
Then, we have
\begin{eqnarray*}
\frac{1}{2} & = & \mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
 & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta\ket{i}+r_{i2}\cos\theta\ket{i}\right)\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
 & = & r_{11}\sin^{2}\theta+r_{12}\cos\theta\rme^{-\rmi\gamma}\sin\theta+r_{21}\rme^{\rmi\gamma}\sin\theta\cos\theta+r_{22}\cos^{2}\theta
\end{eqnarray*}
Because the above equation holds for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=\frac{1}{2}$.\qed\end{example}
\end{document}

>>>>

If we consider $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
example~\ref{ex:three-dimensional-4-value} in appendix~\ref{sec:Examples-for-QuantumIVPM}
provides another example with an empty core. Comparing to example~\ref{ex:three-dimensional-three-value},
example~\ref{ex:three-dimensional-4-value} is closer to the Born
rule in a sense that it might only correspond to $\ket{2}$ or $\frac{\mathbb{1}}{3}$,
but not $\ket{1}$. Example~\ref{ex:three-dimensional-4-value} is
also no longer valid for more precise measurement equipment as well.
In general, we believe if the measurement equipment is more and more
precise, its interval-valued probability measure will be closer and
closer to the the Born rule. In the limit case, $\mathscr{I}=\left\{ \left\{ a\right\} \middle|a\in\left[0,1\right]\right\} $
recovers conventional Gleason's theorem and the Born rule.

@@

\end{pmatrix}=\sqrt{2}\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}

@@

Consider a general density matrix~ $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{2}}\tensor*[_{\mathscr{O}}]{\sum}{_{j=0}^{2}}r_{ij}\ket{i}\bra{j}$.
Then, we have 
\begin{eqnarray*}
\frac{1}{2} & = & \mu_{\rho}^{B}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{0_{\theta,\gamma}^{\perp}}\right)\\
 & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)\left(\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
 & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(r_{i1}\rme^{\rmi\gamma}\sin\theta+r_{i2}\cos\theta\right)\ket{i}\left(\rme^{-\rmi\gamma}\sin\theta\bra{1}+\cos\theta\bra{2}\right)\right)\\
 & = & r_{11}\sin^{2}\theta+r_{12}\cos\theta\rme^{-\rmi\gamma}\sin\theta+r_{21}\rme^{\rmi\gamma}\sin\theta\cos\theta+r_{22}\cos^{2}\theta
\end{eqnarray*}
Because the above equation holds for all $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we must have $r_{12}=r_{21}=0$ and $r_{11}=r_{22}=\frac{1}{2}$.
We also have
\begin{eqnarray*}
\frac{1}{2} & = & \mu_{\rho}^{B}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
 & \stackrel{\left(\ref{BornRule.mixed}\right)}{=} & \Tr\left(\rho\proj{\ps_{\theta,\gamma}^{\perp}}\right)\\
 & = & \Tr\left(\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\sideset{_{\mathscr{O}}}{_{j=0}^{2}}\sum r_{ij}\ket{i}\bra{j}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)\left(-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}\right)^{\dagger}\right)\\
 & = & \Tr\left(\sideset{_{\mathscr{O}}}{_{i=0}^{2}}\sum\left(-\frac{r_{i0}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{i1}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{i2}\cos\theta\right)\ket{i}\left(-\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{0}+\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\bra{1}+\cos\theta\bra{2}\right)\right)\\
 & = & -\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{00}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{r_{01}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+r_{02}\cos\theta\right)+\frac{\rme^{-\rmi\gamma}\sin\theta}{\sqrt{2}}\left(-\frac{r_{10}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{\rme^{\rmi\gamma}\sin\theta}{2\sqrt{2}}\right)\\
 &  & +\cos\theta\left(-\frac{r_{20}\rme^{\rmi\gamma}\sin\theta}{\sqrt{2}}+\frac{\cos\theta}{2}\right)\\
 & = & \left(\frac{r_{00}\sin^{2}\theta}{2}-\frac{r_{01}\sin^{2}\theta}{2}-\frac{r_{02}\rme^{-\rmi\gamma}\sin\theta\cos\theta}{\sqrt{2}}\right)+\left(-\frac{r_{10}\sin^{2}\theta}{2}+\frac{\sin^{2}\theta}{4}\right)+\left(-\frac{r_{20}\rme^{\rmi\gamma}\cos\theta\sin\theta}{\sqrt{2}}+\frac{\cos^{2}\theta}{2}\right)\\
 & = & \left(\frac{r_{00}}{2}-\frac{r_{01}}{2}-\frac{r_{10}}{2}+\frac{1}{4}\right)\sin^{2}\theta+\frac{\cos^{2}\theta}{2}-\left(r_{02}\rme^{-\rmi\gamma}+r_{20}\rme^{\rmi\gamma}\right)\frac{\cos\theta\sin\theta}{\sqrt{2}}
\end{eqnarray*}
Because of the same reason, we have $r_{02}=r_{20}=0$ and $r_{00}=\frac{1}{2}+r_{01}+r_{10}$.
Moreover, because $\rho$ is a density matrix, we should have $\Tr\left(\rho\right)=1$
and $\rho^{\dagger}=\rho$ so that $r_{00}=0$, $r_{01}=-\frac{1}{4}+\rmi b$,
and $r_{01}=-\frac{1}{4}-\rmi b$, where $b\in\mathbb{R}$. However,
it is easy to verify that $\rho$ will have a negative eigenvalue.
This contradicts to the fact that $\rho$ as a a density matrix must
be a positive operator.\qed\end{example} 
\end{document}
